### 2020-08-16 thesis/chap_1.tex
updates chap1 auc values
fix all ordination figures

% PCA
\begin{figure}[h!]
  \centering
    \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_data_profiles.png}
  \caption{Ordination of land use data (proportions) for municipalities. Groups are derived from clustering in figure \ref{fig:clustervals}.}
  \label{fig:PCAvals}

% MAP
  \centering
    \includegraphics[width=\textwidth]{thesis/figures/profiles_land_use.png}
  \caption{Geographical distribution of the 5 profiles identified in figures \ref{fig:clustervals} and \ref{fig:PCAvals}.}
  \label{fig:mapvals}
\end{figure}

@@

% PCA
\begin{figure}[h!]
  \centering
    \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_trans_profiles.png}
  \caption{Ordination of land use transition data for municipalities. Groups are derived from clustering in figure \ref{fig:clustertrans}.}
  \label{fig:PCAtrans}

%MAP
  \centering
    \includegraphics[width=\textwidth]{thesis/figures/transition_prof_map.png}
  \caption{Geographical distribution of the 4 change profiles identified in figures \ref{fig:clustertrans} and \ref{fig:PCAtrans}.}
  \label{fig:maptrans}
\end{figure}

@@

%\begin{table}[!htbp] \centering
\caption{AUC and average precision values for the predictions of the land use change model.} 
\label{tab:historic_metrics} 
\begin{tabular}{lcccc}
\hline
\hline
\multicolumn{1}{c}{Model} & \begin{tabular}[c]{@{}c@{}}Mean AUC\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean AUC +/- Std\\ (All Iterations \\ Averaged)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision +/- Std\\ (All Iterations \\ Averaged)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Agricultural \\ Expansion\end{tabular} & $0.858$ & $0.383$ & $0.669 \pm 0.001$ & $0.105 \pm 0.001$ \\
Urbanisation & $0.784$ & $0.287$ & $0.618 \pm 0.001$ & $0.102 \pm 0.001$ \\ \hline
\end{tabular}
\end{table}

>>>>

% PCA
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_data_profiles.png}
}
\caption{Ordination of land use data (proportions) for municipalities. Groups are derived from clustering in figure \ref{fig:clustervals}.}
\label{fig:PCAvals}

% MAP
\makebox[\textwidth]{
    \includegraphics[width=0.9\textwidth]{thesis/figures/profiles_land_use.png}
}
\caption{Geographical distribution of the 5 profiles identified in figures \ref{fig:clustervals} and \ref{fig:PCAvals}.}
\label{fig:mapvals}
\end{figure}

@@

% PCA
\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=0.9\textwidth]{thesis/figures/PCA_trans_profiles.png}
}
\caption{Ordination of land use transition data for municipalities. Groups are derived from clustering in figure \ref{fig:clustertrans}.}
\label{fig:PCAtrans}

%MAP
\makebox[\textwidth]{
    \includegraphics[width=0.9\textwidth]{thesis/figures/transition_prof_map.png}
}
\caption{Geographical distribution of the 4 change profiles identified in figures \ref{fig:clustertrans} and \ref{fig:PCAtrans}.}
\label{fig:maptrans}
\end{figure}

@@

%\begin{table}[!htbp] \centering
\caption{AUC and average precision values for the predictions of the land use change model.} 
\label{tab:historic_metrics} 
\begin{tabular}{lcccc}
\hline
\hline
\multicolumn{1}{c}{Model} & \begin{tabular}[c]{@{}c@{}}Mean AUC\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision\\ (Averaged \\ Surface)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean AUC +/- Std\\ (All Iterations \\ Averaged)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Mean Precision +/- Std\\ (All Iterations \\ Averaged)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}l@{}}Agricultural \\ Expansion\end{tabular} & $0.858$ & $0.383$ & $0.678 \pm 0.002$ & $0.109 \pm 0.002$ \\
Urbanisation & $0.784$ & $0.287$ & $0.647 \pm 0.001$ & $0.135 \pm 0.001$ \\ \hline
\end{tabular}
\end{table}
